---
title: "hw01_gapminder"
author: "Nima"
date: "9/15/2019"
output: github_document
---


```{r, echo=FALSE}
library(gapminder)
```




Here is a summary of life expectancy, population and GDP per capita of countries in Asia:

```{r , echo= FALSE}
Asia <- gapminder[which(gapminder$continent=="Asia"),]
summary(Asia[,4:6])
```

Here you can see the summary of the same variables for Iran:

```{r ,echo=FALSE}
Iran <- gapminder[which(gapminder$country=="Iran"),]
summary(Iran[,4:6])
```

__Are life expectancy, population and GDP per capita of Iran higher than the average of countries in Asia?__

```{r comparison, echo= FALSE}
c1 <- mean(Iran$lifeExp)>mean(Asia$lifeExp)
c2 <- mean(Iran$pop)>mean(Asia$pop)
c3 <- mean(Iran$gdpPercap)>mean(Asia$gdpPercap)
c <- c(c1,c2,c3)
cc <- c("","","")
for (i in 1:3){ifelse(c[i]==TRUE,cc[i] <- "greater",cc[i] <- "less") 
  }

```
As you can see from the above:

- The average of life expectancy in Iran is `r cc[1]` than the average of countries in Asia.

- The average of population in Iran is `r cc[2]` than the average of countries in Asia.

- The average of GDP per capita in Iran is `r cc[3]` than the average of countries in Asia.

```
